Pteropod biomarker analysis

### 2018-03-01 eval.Rmd
removed latitude, sal, ta, fluor, co3
fixed pairs plot with envchr, biochr select

envchr <- c('Ara', 'O2', 'pH', 'Fluor', 'CO3', 'pCO2', 'Sal', 'TA', 'Temp', 'Latitude')
biochr <- c('CAT', 'GR', 'GSHonGSSG', 'GST', 'LPX', 'ORAC', 'SOD', 'ORACvLPX')
```

Pairs plot of biomarkers and environmental data
```{r, fig.height = 8, fig.width = 8}
dat <- biodat %>% 
  left_join(envdat, by = 'CTD') %>% 
  mutate_if(is.character, as.numeric) %>% 
  gather('var', 'val', -CTD) %>% 
  group_by(CTD, var) %>% 
  summarise(val = mean(val, na.rm = TRUE)) %>% 
  ungroup %>% 
  spread(var, val)

>>>>

envchr <- c('Ara', 'O2', 'pH', 'pCO2', 'Temp')
biochr <- c('CAT', 'GR', 'GSHonGSSG', 'GST', 'LPX', 'ORAC', 'SOD', 'ORACvLPX')
```

Pairs plot of biomarkers and environmental data
```{r, fig.height = 8, fig.width = 8}
dat <- biodat %>% 
  left_join(envdat, by = 'CTD') %>% 
  mutate_if(is.character, as.numeric) %>% 
  select(one_of(c(envchr, biochr, 'CTD'))) %>% 
  gather('var', 'val', -CTD) %>% 
  group_by(CTD, var) %>% 
  summarise(val = mean(val, na.rm = TRUE)) %>% 
  ungroup %>% 
  spread(var, val)
